### 2018-09-02 paper/preliminaries.tex
small suggestions

@@

A prefixing operator $e \then P$ defines a process that is ready to engage in
the event $e$, pending agreement of its environment to synchronising. After
$e$ occurs, the process behaves as defined by $P$. The environment can be
other processes, in parallel, or the environment of a system as a whole.

Two forms of choice support branching behaviour. An external choice $P
\extchoice Q$ between processes $P$ and $Q$ offers to the environment the
initial events of $P$ and $Q$. Once synchronisation takes place, the process
that offered this event is chosen and the other is discarded. In an internal
choice $P \intchoice Q$, the environment does not have an opportunity to
interfere:~the choice is made by the process itself.

\begin{example}\label{example:CSP}
  We consider $P$, $Q$, and $R$ below. $P$ is initially
  ready to engage in the event $a$, and then makes an internal  choice to
  behave like either $Q$ or $R$.
  \begin{eqnarray*}
  P & = & a \then (Q\intchoice R)
  \\
  Q & = & a \then P \extchoice c \then P
  \\
  R & = & b \then P \extchoice c \then R
  \end{eqnarray*}
  $Q$, for instance, offers to the environment the choice to engage in $a$
  again or $c$. In both cases, afterwards, we have a recursion back to $P$.
  In $R$, if $b$ is chosen, we also have a recursion back to $P$. If $c$ is
  chosen, the recursion is to $R$.
  \xbox
\end{example}
%
Iterated forms $\Extchoice i: I @ P(i)$ and $\Intchoice i: I @ P(i)$ of the
external and internal choice operators allow us to define a choice over a
collection of processes $P(i)$. By convention, external choices evaluate to
the process $\Stop$, which deadlocks:~does not engage into any event and does
not terminate, if the index set $I$ is empty. An iterated internal choice is
not defined for an empty index set.

@@

Interactions that are not supposed to be visible to the environment can be
hidden. The operator $P \hide H$ defines a process that behaves as $P$, with
the interactions modelled by events in the set $H$ hidden. Frequently, hiding
is used in conjunction with parallelism:~it is often desirable to make
internal actions of each process in a network of parallel processes , perhaps
used for coordination of the network, invisible, while events happening at
their interfaces remain observable.

@@

Using the notation $P/s$ to denote the process $P$ after having engaged into
trace $s$, the set $\refs(P/s) \defs \{~X | (s,X) \in \fails(P)~\}$ contains
the  refusals of $P$ after the trace $s$. Refusals are
subset-closed~\cite{Hoare:1985:CSP:3921,Roscoe2010}: if $(s,X)$ is a failure
of $P$ and $Y\subseteq X$, then $(s,Y)\in\fails(P)$ and $Y\in\refs(P/s)$
follows.

Failures refinement, $P \lessdet_F Q$, is defined as expected by set
containment $\fails(Q)\subseteq\fails(P)$. Since refusals are subset-closed,
$(s,\varnothing)\in\fails(P)$ for all traces $s\in\trc(Q)$. As a
consequence, failures refinement implies trace refinement. Therefore, using
the auxiliary conformance relation
\begin{equation}\label{eq:conf}
  Q\ conf\ P \defs \forall s\in \trc(P) \cap \trc(Q): \refs(Q/s)
  \subseteq \refs(P/s),
\end{equation}
failures refinement can be expressed by $\lessdet_T$ and $conf$.
\begin{equation}\label{thm:fref-tref-conf}
(P \lessdet_F Q) \iff (P \lessdet_T Q \land Q\ conf\ P)
\end{equation}
%
Throughout this paper, the alphabet of the processes, that is the set of
events that are in scope, is denoted by $\Sigma$ and supposed to be finite.
%Since we are only
%considering ``classical'' CSP processes, the alphabet is always finite.
The FDR tool~\cite{fdr} supports model checking and semantic analyses of
finite-state CSP processes.

>>>>

In this section, we present CSP and the concept of minimal hitting set, which
is central to our novel notion of test for failures refinement.

@@

A prefixing operator $e \then P$ defines a process that is ready to engage in
the event $e$, pending agreement of its environment to synchronise. After $e$
occurs, the process behaves as defined by $P$. The environment can be other
processes, in parallel, or the environment of a system as a whole.

Two forms of choice support branching behaviour. An external choice $P
\extchoice Q$ between processes $P$ and $Q$ offers to the environment the
initial events of $P$ and $Q$. Once synchronisation takes place, the process
that has offered this event is chosen and the other is discarded. In an
internal choice $P \intchoice Q$, the environment does not have an
opportunity to interfere:~the choice is made by the process.
%
\begin{example}\label{example:CSP}
  We consider $P$, $Q$, and $R$ below. $P$ is initially
  ready to engage in the event $a$, and then makes an internal  choice to
  behave like either $Q$ or $R$.
  \begin{eqnarray*}
  P & = & a \then (Q\intchoice R)
  \\
  Q & = & a \then P \extchoice c \then P
  \\
  R & = & b \then P \extchoice c \then R
  \end{eqnarray*}
  $Q$, for instance, offers to the environment the choice to engage in $a$
  again or $c$. In both cases, afterwards, we have a recursion back to $P$.
  In $R$, if $b$ is chosen, we also have a recursion back to $P$. If $c$ is
  chosen, the recursion is to $R$.
  \xbox
\end{example}
%
Iterated forms $\Extchoice i: I @ P(i)$ and $\Intchoice i: I @ P(i)$ of the
external and internal choice operators allow us to define a choice over a
collection of processes $P(i)$. By convention, , if the index set $I$ is
empty, external choices evaluate to the process $\Stop$, which
deadlocks:~does not engage into any event and does not terminate. An iterated
internal choice is not defined for an empty index set. \fixme{alcc: Note the
difference to internal choice. I think this is not a problem here.}

@@

Interactions that are not supposed to be visible to the environment can be
hidden. The operator $P \hide H$ defines a process that behaves as $P$, with
the interactions modelled by events in the set $H$ hidden. Frequently, hiding
is used in conjunction with parallelism:~it is often desirable to make
internal actions of each process in a network of parallel processes, perhaps
used for coordination of the network, invisible, while events happening at
their interfaces remain observable.

@@

Using the notation $P/s$ to denote the process $P$ after having engaged into
trace $s$, the set $\refs(P/s) \defs \{~X | (s,X) \in \fails(P)~\}$ contains
the  refusals of $P$ after $s$. Refusals are
subset-closed~\cite{Hoare:1985:CSP:3921,Roscoe2010}: if $(s,X)$ is a failure
of $P$ and $Y\subseteq X$, then $(s,Y)\in\fails(P)$ and $Y\in\refs(P/s)$
follows.

Failures refinement, $P \lessdet_F Q$, is defined as expected by set
containment $\fails(Q)\subseteq\fails(P)$. Since refusals are subset-closed,
$(s,\varnothing)\in\fails(P)$ for all traces $s\in\trc(Q)$. So, for
divergences-free processes, failures refinement implies trace refinement.
Therefore, using the conformance relation $conf$ 
\begin{equation}\label{eq:conf}
  Q\ conf\ P \defs \forall s\in \trc(P) \cap \trc(Q): \refs(Q/s)
  \subseteq \refs(P/s),
\end{equation}
failures refinement can be expressed by $\lessdet_T$ and $conf$.
\begin{equation}\label{thm:fref-tref-conf}
(P \lessdet_F Q) \iff (P \lessdet_T Q \land Q\ conf\ P)
\end{equation}
%
Throughout this paper, the alphabet of the processes, that is the set of
events that are in scope, is denoted by $\Sigma$ and supposed to be finite.
%Since we are only
%considering ``classical'' CSP processes, the alphabet is always finite.
The FDR tool~\cite{fdr} supports model checking and semantic analyses of
finite-state CSP processes.
